On exponential sums arising from the classical doubling method

### 2025-03-20 paper.tex
Typo

\begin{remark}
	Changing variables $x \mapsto \to x$, we have that \begin{align*}
		& \sum_{\substack{x \in \multiplicativegroup{\finiteFieldExtension{k}}\\
				x \ne -1}} \alpha \left(x\right) \chi\left(\FieldNorm{k}{1}\left(1 + x\right)\right) \chi\left(\FieldNorm{k}{1}\left(1 + \minusInvolution{x}\right)\right) \\
			=& -q^{\frac{k}{2}} \GaussSumCharacter{\alpha^{-1}}{\chi^{-1}}{\fieldCharacter_{\quadraticFieldExtension{k}}} \GaussSumCharacter{\involution{\alpha}}{\chi^{-1}}{\fieldCharacter_{\quadraticFieldExtension{k}}} \tau\left(\involutionPlusOne{\chi}, \fieldCharacter_{\quadraticExtension}\right)^k.
	\end{align*}
\end{remark}

>>>>

\begin{remark}
	Changing variables $x \mapsto -x$, we have that \begin{align*}
		& \sum_{\substack{x \in \multiplicativegroup{\finiteFieldExtension{k}}\\
				x \ne -1}} \alpha \left(x\right) \chi\left(\FieldNorm{k}{1}\left(1 + x\right)\right) \chi\left(\FieldNorm{k}{1}\left(1 + \minusInvolution{x}\right)\right) \\
			=& -q^{\frac{k}{2}} \GaussSumCharacter{\alpha^{-1}}{\chi^{-1}}{\fieldCharacter_{\quadraticFieldExtension{k}}} \GaussSumCharacter{\involution{\alpha}}{\chi^{-1}}{\fieldCharacter_{\quadraticFieldExtension{k}}} \tau\left(\involutionPlusOne{\chi}, \fieldCharacter_{\quadraticExtension}\right)^k.
	\end{align*}
\end{remark}
